The Galaxy Cluster Merger Catalog: An Online Repository of Mock Observations from Simulated Galaxy Cluster Mergers

### 2016-09-08 paper/ms.tex
More text for paper

The galaxy cluster merger simulation data in the catalog comes from state-of-the-art N-body and hydrodynamics codes such as FLASH and Athena. The exact physics and algorithms employed by the simulations vary, but in general:

@@

The projected data is generated from the original simulation data using yt \citep{tur11}.

AstroPy \citep{apy13} is used to generate the data outputs in the (FITS) data format \citep{pen10} and generate coordinates for the files using the World Coordinate System \citep[WCS,][]{gre02, cal02} specification.

@@

@@

With the exception of the X-ray event files, no attempt is made in the mock observations to include statistical and systematic errors on the observed quantities, instrumental effects, or background contamination. It is not possible to anticipate what assumptions the end-user may want to make about these issues, so these effects have been left out so they may be added on a case-by-case basis for different situations.

@@

\begin{itemize}
\item \code{"xray\_emissivity"}: X-ray photon surface brightness in the 0.5-7.0~keV (observer) band, computed using an APEC model, in units of ${\rm photons~s^{-1}~{cm}^{-2}~{arcsec}^{-2}}$. For simulations without metallicity, a spatially constant metallicity of ${\rm Z = 0.3~Z_\odot}$ is assumed.
\item \code{"kT"}: Emission-weighted projected temperature, using the emissivity described above, in units of keV.
\item \code{"total\_density"}: Total mass density (gas and dark matter) in units of $\rm{M_\odot~{kpc}^{-3}}$.
\item \code{"szy"}: The integrated ``y-parameter'' for the thermal Sunyaev-Zeldovich (S-Z) effect, given by
\begin{equation}
y_{\rm tSZ} = \int{\frac{k_BT}{m_e{c^2}}\sigma_T{n_e}{\rm d\ell}}.
\end{equation}
\item \code{"sz\_kinetic"}: The integrated ``y-parameter'' for the kinetic S-Z effect, given by
\begin{equation}
y_{\rm kSZ} = \int{\frac{v_\ell}{c}\sigma_T{n_e}{\rm d\ell}}.
\end{equation}
\item \code{"rotation\_measure"}: Faraday rotation measure in units of rad~m$^{-2}$, given by:
\begin{equation}
{\rm RM} = \frac{e^3}{2\pi{m_e}^2c^4}\int{n_e}{B_{\ell}}{\rm d}{\ell}.
\end{equation}
\end{itemize}

@@

\begin{thebibliography}{}
\bibitem[Astropy Collaboration et al.(2013)]{apy13} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
\bibitem[Berger \& Colella(1989)]{ber89} Berger, M.~J., \& Colella, P.\ 1989, Journal of Computational Physics, 82, 64
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Colella \& Woodward(1984)]{col84} Colella, P., \& Woodward, P.~R.\ 1984, Journal of Computational Physics, 54, 174
\bibitem[Greisen \& Calabretta(2002)]{gre02} Greisen, E.~W., \& Calabretta, M.~R.\ 2002, \aap, 395, 1061
\bibitem[Calabretta \& Greisen(2002)]{cal02} Calabretta, M.~R., \& Greisen, E.~W.\ 2002, \aap, 395, 1077
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[Evans \& Hawley(1988)]{eva88} Evans, C.~R., \& Hawley, J.~F.\ 1988, \apj, 332, 659
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Pence et al.(2010)]{pen10} Pence, W.~D., Chiappetti, L., Page, C.~G., Shaw, R.~A., \& Stobie, E.\ 2010, \aap, 524, A42
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Ricker(2008)]{ric08} Ricker, P.~M.\ 2008, \apjs, 176, 293-300
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908 (ZMJ10)
\bibitem[ZuHone(2011)]{zuh11} ZuHone, J.~A.\ 2011, \apj, 728, 54 (Z11)
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}

>>>>

The galaxy cluster merger simulation data in the catalog comes from state-of-the-art N-body and hydrodynamics codes such as FLASH \citep{dub09} and Athena \citep{sto08}. The exact physics and algorithms employed by the simulations vary, but in general:

@@

The projected data is generated from the original simulation data using yt \citep{tur11}, an open-source Python package for analyzing and visualizing volumetric data. yt has capabilities for slicing and projecting physical fields from multi-resolution datasets such as those from galaxy cluster merger simulations along arbitrary lines of sight. Through analysis modules and affiliated packages, yt also has capabilities to produce synthetic Sunyaev-Zeldovich (S-Z) and X-ray observations. We provide details on how this is done in Sections \ref{sec:sz} and \ref{sec:xray}.

AstroPy \citep{apy13} is used to take the projected data generated in yt and produce data outputs in the standard Flexible Image Transport System (FITS) data format \citep{pen10} and generate coordinates for the files using the World Coordinate System \citep[WCS,][]{gre02, cal02} specification.

@@

JS9 (\url{http://js9.si.edu}) is a browser-based implementation of SAOImage DS9 (\url{http://ds9.si.edu/}), an astronomical imaging and data visualization application. JS9 provides interactive exploration of FITS image and table data including zooming, panning, colormaps, scaling, and region files. On each ``epoch page'' (Section \ref{sec:epoch_page}) there is an interface to JS9 and links to open FITS files from that epoch in the JS9 interface.

@@

With the exception of the X-ray event files (Section \ref{sec:xray}), no attempt is made in the mock observations to include statistical and systematic errors on the observed quantities, instrumental effects, or background contamination. It is not possible to anticipate what assumptions the end-user may want to make about these issues, so these effects have been left out so they may be added on a case-by-case basis for different situations.

@@

\begin{itemize}
\item \code{"xray\_emissivity"}: X-ray photon surface brightness in the 0.5-7.0~keV (observer) band, computed using an APEC model, in units of ${\rm photons~s^{-1}~{cm}^{-2}~{arcsec}^{-2}}$. For simulations without metallicity, a spatially constant metallicity of ${\rm Z = 0.3~Z_\odot}$ is assumed.
\item \code{"kT"}: Emission-weighted projected temperature, using the emissivity described above, in units of keV.
\item \code{"total\_density"}: Total mass density (gas and dark matter) in units of $\rm{M_\odot~{kpc}^{-3}}$.
\item \code{"szy"}: The integrated ``y-parameter'' for the thermal S-Z effect, given by
\begin{equation}
y_{\rm tSZ} = \int{\frac{k_BT}{m_e{c^2}}\sigma_T{n_e}{\rm d\ell}}.
\end{equation}
\item \code{"sz\_kinetic"}: The integrated ``y-parameter'' for the kinetic S-Z effect, given by
\begin{equation}
y_{\rm kSZ} = \int{\frac{v_\ell}{c}\sigma_T{n_e}{\rm d\ell}}.
\end{equation}
\item \code{"rotation\_measure"}: Faraday rotation measure in units of rad~m$^{-2}$, given by:
\begin{equation}
{\rm RM} = \frac{e^3}{2\pi{m_e}^2c^4}\int{n_e}{B_{\ell}}{\rm d}{\ell}.
\end{equation}
\end{itemize}

@@

\begin{thebibliography}{}
\bibitem[Astropy Collaboration et al.(2013)]{apy13} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33
\bibitem[Berger \& Colella(1989)]{ber89} Berger, M.~J., \& Colella, P.\ 1989, Journal of Computational Physics, 82, 64
\bibitem[Br{\"u}ggen et al.(2012)]{bru12} Br{\"u}ggen, M., Bykov, A., Ryu, D., R{\"o}ttgering, H.\ 2012, \ssr, 166, 187
\bibitem[Brunetti \& Lazarian(2007)]{bru07} Brunetti, G., \& Lazarian, A.\ 2007, \mnras, 378, 245
\bibitem[Colella \& Woodward(1984)]{col84} Colella, P., \& Woodward, P.~R.\ 1984, Journal of Computational Physics, 54, 174
\bibitem[Greisen \& Calabretta(2002)]{gre02} Greisen, E.~W., \& Calabretta, M.~R.\ 2002, \aap, 395, 1061
\bibitem[Calabretta \& Greisen(2002)]{cal02} Calabretta, M.~R., \& Greisen, E.~W.\ 2002, \aap, 395, 1077
\bibitem[Clowe et al.(2004)]{clo04} Clowe, D., Gonzalez, A., \& Markevitch, M.\ 2004, \apj, 604, 596
\bibitem[Chluba et al.(2012)]{chl12} Chluba, J., Nagai, D., Sazonov, S., \& Nelson, K.\ 2012, \mnras, 426, 510
\bibitem[Chluba et al.(2013)]{chl13} Chluba, J., Switzer, E., Nelson, K., \& Nagai, D.\ 2013, \mnras, 430, 3054
\bibitem[Donnert et al.(2013)]{don13} Donnert, J., Dolag, K., Brunetti, G., \& Cassano, R.\ 2013, \mnras, 429, 3564
\bibitem[{Dubey} et~al.(2009)]{dub09} {Dubey}, A., {Antypas}, K.,
  {Ganapathy}, M.~K., {Reid}, L.~B., {Riley}, K.~M., {Sheeler}, D.,
  {Siegel}, A., {Weide}, K. Extensible component based architecture
  for FLASH, a massively parallel, multiphysics simulation
  code. Parallel Computing 35~(10-11), 512--522.
\bibitem[Evans \& Hawley(1988)]{eva88} Evans, C.~R., \& Hawley, J.~F.\ 1988, \apj, 332, 659
\bibitem[Feretti(2005)]{fer05} Feretti, L.\ 2005, Advances in Space Research, 36, 729
\bibitem[Ford et al.(2014)]{for14} Ford, J., Hildebrandt, H., Van Waerbeke, L., et al.\ 2014, \mnras, 439, 3755
\bibitem[Forman et al.(1972)]{for72} Forman, W., Kellogg, E., Gursky, H., Tananbaum, H., \& Giacconi, R.\ 1972, \apj, 178, 309
\bibitem[Markevitch et al.(2004)]{mar04} Markevitch, M., Gonzalez, A.~H., Clowe, D., et al.\ 2004, \apj, 606, 819
\bibitem[Pence et al.(2010)]{pen10} Pence, W.~D., Chiappetti, L., Page, C.~G., Shaw, R.~A., \& Stobie, E.\ 2010, \aap, 524, A42
\bibitem[Poole et al.(2006)]{poo06} Poole, G.~B., Fardal, M.~A., Babul, A., McCarthy, I.~G., Quinn, T., \& Wadsley, J.\ 2006, \mnras, 373, 881
\bibitem[Ricker \& Sarazin(2001)]{ric01} Ricker, P.~M., \& Sarazin, C.~L.\ 2001, \apj, 561, 621
\bibitem[Ricker(2008)]{ric08} Ricker, P.~M.\ 2008, \apjs, 176, 293-300
\bibitem[Skillman et al.(2013)]{ski13} Skillman, S.~W., Xu, H., Hallman, E.~J., et al.\ 2013, \apj, 765, 21
\bibitem[Stone et al.(2008)]{sto08} Stone, J.~M., Gardiner, T.~A., Teuben, P., Hawley, J.~F., \& Simon, J.~B.\ 2008, \apjs, 178, 137
\bibitem[Sunyaev \& Zeldovich(1972)]{sun72} Sunyaev, R.~A., \& Zeldovich, Y.~B.\ 1972, Comments on Astrophysics and Space Physics, 4, 173
\bibitem[Turk et al.(2011)]{tur11} Turk, M.~J., Smith, B.~D., Oishi, J.~S., Skory, S., Skillman, S.~W., Abel, T., \& Norman, M.~L.\ 2011, \apjs, 192, 9
\bibitem[van Weeren et al.(2010)]{vwe10} van Weeren, R.~J., R{\"o}ttgering, H.~J.~A., Br{\"u}ggen, M., \& Hoeft, M.\ 2010, Science, 330, 347
\bibitem[Vazza et al.(2009)]{vaz09} Vazza, F., Brunetti, G., Kritsuk, A., et al.\ 2009, \aap, 504, 33
\bibitem[Yu et al.(2015)]{yu15} Yu, L., Nelson, K., \& Nagai, D.\ 2015, \apj, 807, 12
\bibitem[ZuHone et al.(2010)]{zuh10} ZuHone, J.~A., Markevitch, M., \& Johnson, R.~E.\ 2010, \apj, 717, 908 (ZMJ10)
\bibitem[ZuHone(2011)]{zuh11} ZuHone, J.~A.\ 2011, \apj, 728, 54 (Z11)
\bibitem[ZuHone et al.(2014)]{zuh14} ZuHone, J.~A., Biffi, V., Hallman, E.~J., et al.\ 2014, arXiv:1407.1783
\bibitem[Zwicky(1937)]{zwi37} Zwicky, F.\ 1937, \apj, 86, 217
\end{thebibliography}{}
